%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{enumitem}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{\custombold{Pan Deng}}{ 
\href{mailto:pad2016@med.cornell.edu}{pad2016@med.cornell.edu} \\ 347.415.3502
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Cornell University}
\descript{Ph.D., Cell Biology}
\location{Expected Dec 2017}
\sectionsep

\subsection{Tsinghua University}
\descript{BS, Biological Sciences}
\location {Grad. June 2012 \\
Cum. GPA: 89.7 / 100 \\
Rank: 6 / 68}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/OXPHOS}{\custombold{OXPHOS}} \\
LinkedIn://  \href{https://www.linkedin.com/in/pandeng16}{\custombold{PanDeng}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Quantitative Genomics and Genetics \\
Biomedical Machine Learning \\
\sectionsep

\subsection{Undergraduate}
Calculus \\
Linear Algebra and Analytical Geometry \\
Probability and Statistics \\
Stochastic Mathematical Methods \\
C++ Programming \\
\sectionsep

\subsection{Coursera}
Algorithms {\footnotesize \textit{\textbf{(Java)}}} \\
Bioinformatics Algorithms {\footnotesize \textit{\textbf{(Python)}}} \\
Machine Learning {\footnotesize \textit{\textbf{(Matlab)}}} \\
Fundamentals of Computing Specialization {\footnotesize \textit{\textbf{(Python)}}} \\
Cloud Computing Specialization \\
Data Science at Scale Specialization \\
System Biology Specialization \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} Matlab \textbullet{} R \\
C++ \textbullet{} Bash \textbullet{} CMake \\
Java \textbullet{} SQL \textbullet{} \LaTeX \\
\sectionsep


Spark \textbullet{} Hadoop \textbullet{} Docker\\
Numpy \textbullet{} Pandas \textbullet{} Tensorflow \\
Cereal \textbullet{} ViennaCL \textbullet{} Twitter REST 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Summer Intern | Open source contributor} \\
\descript{Shogun Machine Learning Toolbox (C++)}
\location{May 2016 – Present | Google Summer of Code 2016}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Refactored Shogun’s linear algebra library for CPU and GPU backend operations \item	Refactored Shogun’s serialization framework with Cereal \item Finished cookbook pages: K-means clustering, hierarchical clustering, logistic regression, linear machine, QDA, LDA, Gaussian process, ECOC, shareboost, relaxed tree, chaidtree and cartree.
\end{tightemize}
\sectionsep

\runsubsection{Open source contributor} \\
\descript{Pandas Python Data Analysis Toolkit}
\begin{tightemize}\item Reshaped pivot table and cross-tabulation methods. \item	Improved IO of csv file readers.
\end{tightemize}
\sectionsep

\runsubsection{graduate research assistant} \\
\descript{Memorial Sloan Kettering Cancer Center}
\location{Sept 2013 - present | Cole Haynes' Lab}
\begin{tightemize}
\item Analyzed RNA-sequencing data using Bash, R and Python with STAR, samtools, featureCounts, DESeq2 \item Genome-wide mitochondrial targeting prediction in C. elegans with Python \item Genome-wide transcription factor binding motifs prediction with Python
\end{tightemize}
\sectionsep

\runsubsection{graduate research assistant} \\
\descript{Memorial Sloan Kettering Cancer Center}
\location{Jan 2013 – March 2013 | Joao Xavier's Lab}
\begin{tightemize}
\item 
Modeled branching pattern of P. aeruginosa population with Matlab \\
 { \custombold{(Published. 2014 highlights in the New Journal of Physics)}}

\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HONORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{HONORS} 
\begin{tabular}{rll}
2016 &Frank Lappin Horsfall Jr., Student Fellowship 
&MSKCC	\\
2012 &Graduate with Honor &Tsinghua University \\
2012 &Distinguished Dissertation &Tsinghua University \\
2009-2012 & Comprehensive Scholarship &Tsinghua University \\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item \custombold{Deng, P.}, de Vargas Roditi, L., van Ditmarsch, D., and Xavier, J. B. (2014). The ecological basis of morphogenesis: branching patterns in swarming colonies of bacteria. New journal of physics. \\
\item  Nargund, A. M., Fiorese, C. J., Pellegrino, M. W., \custombold{Deng, P.}, and Haynes, C. M. (2015). Mitochondrial and Nuclear Accumulation of the Transcription Factor ATFS-1 Promotes OXPHOS Recovery during the UPRmt. Molecular cell. \\
\item  \custombold{Deng, P.}, and Haynes, C. M. (2016). The mitokine quest (ion). Cell Research. \\
\item  \custombold{Deng, P.}, and Haynes, C. M. (In press). Mitochondrial dysfunction in cancer: Potential roles of the mitochondrial UPR. Seminars in Cancer Biology.
\end{enumerate}
\sectionsep

\end{minipage} 
\end{document}