%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{HCDS_template_resume}
\usepackage{enumitem}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{\textbf{Pan Deng}} \\
\descript{\href{mailto:pad2016@med.cornell.edu}{pad2016@med.cornell.edu}}
\descript{347.415.3502}
\makebox[\linewidth][l]{\rule{0.8\textwidth}{0.8pt}}
\vspace{0.1pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Cornell University}
\descript{Ph.D., Cell Biology}
\location {Expected Mar 2018 \\
GPA: 4.0/4.0 \\ - Frank Lappin Horsfall Jr., Student Fellowship
}
\sectionsep

\subsection{Tsinghua University}
\descript{BS, Biological Sciences}
\location {Grad. June 2012 \\
Cum. GPA: 89.7 / 100 \\
Rank: 6 / 68 \\
- Graduate with Honor \\
- Distinghuished Dissertation}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/OXPHOS}{{OXPHOS}} \\
LinkedIn://  \href{https://www.linkedin.com/in/pandeng16}{{PanDeng}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Quantitative Genomics and Genetics \\
Biomedical Machine Learning \\
\sectionsep

\subsection{Undergraduate}
Calculus \\
Linear Algebra and Analytical Geometry \\
Probability and Statistics \\
Stochastic Mathematical Methods \\
C++ Programming \\
\sectionsep

\subsection{Coursera}
Algorithms {\footnotesize \textit{\textbf{(Java)}}} \\
Bioinformatics Algorithms {\footnotesize \textit{\textbf{(Python)}}} \\
Machine Learning {\footnotesize \textit{\textbf{(Matlab)}}} \\
Fundamentals of Computing Specialization {\footnotesize \textit{\textbf{(Python)}}} \\
Cloud Computing Specialization \\
Data Science at Scale Specialization \\
System Biology Specialization \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
Python \textbullet{} C++ \textbullet{} SQL/NoSQL \\
Matlab \textbullet{} R \textbullet{} JAVA \textbullet{} \LaTeX \\
\sectionsep

Bash \textbullet{} CMake \textbullet{} Git \\
Valgrind  \textbullet{}  Docker \\
\sectionsep
Numpy \textbullet{} Pandas \textbullet{} Scikit-learn \\
\sectionsep
Apache  MapReduce \textbullet{} HDFS \textbullet{} Hive \\
Apache Spark \\
Hortonworks \textbullet{} Cloudera \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{1mm}
\section{Experience}

\runsubsection{Core Maintainer  | Google Summer of Code Mentor} \\
\vspace{1.5pt}
\descript{Shogun Machine Learning Toolbox (C++)}
\location{May 2016 -€“ Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Unified the interface to Shogun's data storage and linear algebra operations on CPU and GPU backends
\item Implemented plug-in based object-oriented linear algebra library supporting algebra operations interfacing from Eigen and ViennaCL
\item Enabled automatic check, download and installation of Cereal serialization library via CMake
\item Implemented interface to Cereal serialization library in Shogun 
\item Documented Shogun's machine learning algorithms, including K-means clustering,hierarchical clustering,logistic regression, linear machine, QDA, LDA, Gaussian process, ECOC, shareboost, relaxed tree, chaidtree and cartree, via Sphinx and meta language generator of Shogun
\end{tightemize}

\vspace{3pt}
\runsubsection{Open source contributor} \\
\vspace{1.5pt}
\descript{Pandas Python Data Analysis Toolkit}
\location{May 2016 -€“ Present}
\begin{tightemize}
\item Fixed key error and value errors bugs in pandas core package
\item	Unified the default \code{N/A} values in I/O package via decorators
\end{tightemize}

\vspace{3pt}
\runsubsection{graduate research assistant} \\
\vspace{1.5pt}
\descript{Memorial Sloan Kettering Cancer Center | Cole Haynes' Lab}
\location{Sept 2013 - present }
\begin{tightemize}
\item Examing virulence-mediated suppression of the mitochondrial stress response upon infection of opportunistic pathogen P. aeruginosa
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PROJECTS} 
\runsubsection{Steam-based game recommender system} | \location{2017}
\vspace{1.5pt}
\begin{tightemize}
\item \fontsml{Implemented html webpage crawler with Python}
\item \fontsml{ Completed data ETL and user-specific game recommendation system with Spark SQL and MLlib (PySpark)}
\\
\end{tightemize}

\vspace{3pt}
\runsubsection{Genome-wide gene differential expression analysis of \textit{C. elegans} during mitochondrial stress} \\
\vspace{1.5pt}
\begin{tightemize}
\item \fontsml {Aligned 8GB+ raw data from C. elegans deep sequencing to reference genome via command line tools STAR, samtools and featureCounts}
\item \fontsml{Normalized and transformed gene expression data with R package DESeq2}
\item \fontsml{Predicted the differential expression of genes and its significance with DESeq2 in R and pandas in Python}
\end{tightemize}

\vspace{3pt}
\runsubsection{Analysis of Casual Polymorphisms Regulating Gene CG9186
\vspace{1.5pt}
Expression in \textit{D. melanogaster}} \\
\begin{tightemize}
\item
\fontsml{Identified genetic variants regulating CG9186 expression with Genome-Wide Association Studies (GWAS) in R}
\end{tightemize}
\vspace{3pt}
\runsubsection{Microbe population branching pattern modeling}
\vspace{1.5pt}
\begin{tightemize}
\item 
\fontsml{Simulated the branching behavior of P. aeruginosa population with spatial kernel approach and cellular automaton model in Matlab with data obtained from biological experiments} \\
 { \textbf{(Published. 2014 highlights in the New Journal of Physics)}}
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS AND CONFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications | Conferences} 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item \fontsml{\textbf{Deng, P.}, et al. (2014). The ecological basis of morphogenesis: branching patterns in swarming colonies of bacteria. New journal of physics. }\\
\item  \fontsml{\textbf{Deng, P.}, et al. (2015). Mitochondrial and Nuclear Accumulation of the Transcription Factor ATFS-1 Promotes OXPHOS Recovery during the UPRmt. Molecular cell.} \\
\item  \fontsml{\textbf{Deng, P.}, and Haynes, C. M. (2016). The mitokine quest (ion). Cell Research.} \\
\item  \fontsml{\textbf{Deng, P.}, and Haynes, C. M. (In press). Mitochondrial dysfunction in cancer: Potential roles of the mitochondrial UPR. Seminars in Cancer Biology.}
\item \fontsml{ \textbf{Poster presentation, Cell Symposia: Multifaceted Mitochondria}, Chicago, IL 2015} \\
\item  \fontsml{\textbf{CppCon'17 Ligtning Talk presenter}, Seattle, WA, 2017} \\
\end{enumerate}
\end{minipage} 
\end{document}